### 2017-07-22 01-intro.tex
Rewrite 2nd bulleted contrib in intro

\item \textbf{scaling out to overcome the memory bounds} posed by 
single-machine systems. Our implementation is the first to solve the largest publicly available
community graphs. % This necessitated overcoming several challenges.
% The algorithm's state grows rapidly with larger graphs and number of latent
% communities.
Since the full state for the larger graphs does not fit in a
single machine's memory, it is partitioned across a cluster
of machines. Hence, the cluster nodes must read
remote memory hosted by their peers. Since the algorithm is data-bound, we
substantially optimized remote memory accesses by implementing
a custom RDMA store.
On top of that, we pipelined the algorithm stages by prefetching
data over the network.
\begin{comment} Finally, the algorithm's computation
is effectively distributed across the cluster nodes and parallelized further
within each node by exploiting their multi-core CPUs.
\end{comment}

>>>>

\item \textbf{scaling out to overcome the memory bounds} posed by
GPUs which are highly effective when the problem state
fits in GPU memory. In order to address larger graphs and numbers of communities,
we created another implementation
that partitions the state across a cluster of machines. This allows processing
much larger problem instances at the cost of (memory) speed, because the
cluster nodes must read remote memory hosted by their peers. Since the
algorithm is data-bound, we substantially optimized remote memory accesses
by implementing a custom RDMA store.
On top of that, we pipelined the algorithm stages by prefetching
data over the network.
\begin{comment} Finally, the algorithm's computation
is effectively distributed across the cluster nodes and parallelized further
within each node by exploiting their multi-core CPUs.
\end{comment}
This implementation is the first to solve the largest publicly available
community graphs.
